### 2022-08-25 manuscript.Rmd
Default to not re-run anything
Update author note

  The authors declare no competing financial interests.
  The materials and code for this study are available at [https://osf.io/uksbc](https://osf.io/uksbc).

@@

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = TRUE,
  mixed_models = TRUE,
  control_analysis = TRUE
)

>>>>

  Number of pages: 23

  Number of figures: 4

  Number of tables: 0

  Number of words: ??? (abstract), ??? (introduction), ??? (discussion)

  The authors declare no competing financial interests.

  We would like to thank Nele Langosch for assistance with data collection and analysis as well as Guido Kiecker for technical support.
  The materials and code for this study are available at [https://osf.io/uksbc](https://osf.io/uksbc).

@@

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = FALSE,
  mixed_models = FALSE,
  control_analysis = FALSE
)
